Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
added figures for tries to paper

@@

>>>>

\begin{figure}[h!]
  \centering
   \includegraphics[scale=.35]{trie_figure}
  \caption{Structure of a trie index with two input tweets. The tweets are first tokenized and stop words are removed. Note that document ids are stored in every node. An artificial root node is created as the root of the trie.}
\end{figure}

@@

\begin{figure}[h!]
  \centering
   \includegraphics[scale=.35]{trie_maxdepth_figure}
  \caption{Structure of a trie index with a maximum depth of 4. If a word gets cut off by the depth limit, the substring remainder is stored at the leaves. Each substring remainder maps to a list of document ids with that remainder.}
\end{figure}
